\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}

### 2014-09-08 pkg/partykit/inst/mloss/letter_mloss2.tex
resubmission letter
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@609 255f4249-2263-4417-b1ea-8498779e27a7

\subject{JMLR-MLOSS submission}

@@

my co-author Achim Zeileis and I would like to submit the manuscript
``\textbf{partykit}: An Open-Source Toolkit for Recursive Partytioning in R'' to the
Machine Learning Open-Source Software track of the Journal of Machine
Learning Research.
The \textsf{R} add-on package \textbf{partykit} described in this submission implements a
flexible toolkit for learning, representing, summarizing, and visualizing a
wide range of tree-structured models.  The package offers a basic class
infrastructure for representing fitted trees, a unified set of methods for
printing and plotting of trees as well as for computing predictions for new
observations, tailored functionality for trees with constant fits and with
parametric models in each terminal node, and reimplementations of conditional
inference trees (CTree) and model-based recursive partitioning (MOB).

This manuscript is related to JMLR-07-240-1 ``Let's Have a party! An
Open-Source Toolbox for Recursive Partytioning'' describing the
\textbf{party} add-on
package.  This manuscript was rejected with encouragement for resubmission by
JMLR-MLOSS editor Cheng Soon Ong in November 2007.  The main concerns of the
reviewers were that it was not easy to extend the old \textbf{party} package by adding
new tree learners or representing existing trees in our package.  This was
a very important suggestion and part of the motivation for starting from
scratch and develop a new R package (\textbf{partykit}) that easily allows to
accommodate our own tree algorithms but makes the underlying infrastructure
easily accessible to others. Actually, the \textbf{partykit} package in its current
form goes well beyond what was suggested in the reviews of JMLR-07-240-1
and both manuscript and software were entirely rewritten. Hence, we felt it
to be more appropriate to submit this as a new manuscript rather than a
revision of JMLR-07-240-1.  However, if you would like to see a formal
point-to-point reply to the old submission, please let us know.

The package web page is \texttt{http://CRAN.R-project.org/package=partykit}
and currently points to version 0.8-0 distributed under the GPL (2 or 3).
This version is also uploaded for review.

>>>>

\subject{JMLR-14-133 resubmission}

@@

my co-author Achim Zeileis and I would like to resubmit the manuscript
``\textbf{partykit}: An Open-Source Toolkit for Recursive Partytioning in R'' to the
Machine Learning Open-Source Software track of the Journal of Machine
Learning Research.

We would like to thank the referees for their constructive reviews and
action editor Cheng Soon Ong for overseeing the review process. While
preparing this resubmission, we took all issues discussed by the referees
into account and revised both the \emph{partykit} package and the four-page
description. A detailed description of our revision can be found in the
point to point reply.

The package web page is \texttt{http://CRAN.R-project.org/package=partykit}
and points to the revised version 0.8-1 distributed under the GPL (2 or 3).
This version is also uploaded for review.
